\section{Work Experience}

\cventry
{Dev Part Lead} % Job Title
{Corca, Inc.} % Organization
{Seoul, Korea} % Location
{12/2022 -} % Date
\begin{cvitems}
\item {Leading the development team.}
\end{cvitems}

\cventry
{MLOps Engineer} % Job Title
{} % Organization
{} % Location
{07/2021 - 12/2022} % Date
\begin{cvitems}
\item {Took charge of MLOps related works.}
\item {Built pipelines for data processing, continuous integration, deployment and training.}
\item {Designed and developed high-performance language-neutral ML Model server using gRPC and protobuf.}
\item {Developed real-time data stream with Kafka streams, processing \textasciitilde 300k messages per minute.}
\item {Implemented event driven architecture where Nest.js servers and Go clients are participating, using Redis.}
\item {Managed infrastructures with Pulumi.}
\item {Successfully handled \textasciitilde 300k requests per minute.}
\end{cvitems}

\cventry
{Backend Developer} % Job Title
{Pangea, Inc.} % Organization
{Seoul, Korea} % Location
{10/2021 - 12/2021} % Date
\begin{cvitems}
\item {Developed and deployed the LINE Blockchain based NFT marketplace based on K-Pop idol contents. (https://momentofartist.com)}
\item {RESTful API with Nest.js.}
\item {Web frontend with React, Next.js, redux-saga.}
\item {Managed devOps related works to serve stably for over 15K users.}
\item {AWS ECS, AWS ElastiCache, MongoDB Atlas, CloudFlare, etc.}
\end{cvitems}

\cventry
{Blockchain Developer} % Job Title
{Mars Green} % Organization
{Seoul, Korea} % Location
{07/2021 - 09/2021} % Date
\begin{cvitems}
\item {Developed Smart Contract and web backend for the etherium based NFT gallery 'Mars Green' (https://marsgreen.co).}
\item {Wrote Smart Contract with Solidity and web backend with express.js and ethers.js.}
\item {Connected the Smart Contract and the web server to make continuous tracking and managing through the web site possible.}
\item {Deployed and maintained the service with AWS ECS Fargate.}
\item {Built the CI/CD pipeline with AWS CodePipeline.}
\end{cvitems}

\cventry
{Web Full Stack Developer} % Job Title
{CodeWings, Inc.} % Organization
{Seoul, Korea} % Location
{12/2020 - 07/2021} % Date
\begin{cvitems}
\item {Developed, deployed and maintained the algorithm education platform web service.}
\item {Designed a well-organized REST API with Django RESTful Framework.}
\item {Connected micro-service to each other with gRPC and socket.io.}
\item {Improved frontend of the site to be more interactive and intuitive with Next.js and redux.}
\item {Deployed server using AWS ECS Fargate, EC2, and CodePipeline.}
\end{cvitems}
