\section{Extra-curricular Activities}

\cventry
{Executive member} % Job Title
{DevKor} % Organization
{Seoul, Korea} % Location
{02/2021 - 02/2022} % Date
\begin{cvitems}
\item {Lectured about web backend developing at software development society of Korea University, DevKor, for students of the university in various of major.}
\item {Held an Hackathon for the students, sponsored by 6 companies including AWS and Naver D2.}
\item {Developed and managed the platform for the event. (https://devk.or.kr)}
\end{cvitems}

\cventry
{Executive member} % Job Title
{CyKor} % Organization
{Seoul, Korea} % Location
{09/2019 - 12/2020} % Date
\begin{cvitems}
\item {Participated many hacking competitions such as DEFCON, CODEGATE, zer0pts as a member of the hacking team, CyKor.}
\item {Lectured about web security and hacking techniques at cyber security society of Korea University, CyKor, for students of Department of Cyber Security.}
\item {Held a CTF as a member of the team CyKor. More than a hundred of competitor participated.}
\item {Developed a platform for the competition. Served and managed tens of challenges made by me and my teammates with docker and three on-premise linux machines}
\end{cvitems}

\cventry
{Penetration Tester} % Job Title
{Contract Research Project} % Organization
{Seoul, Korea} % Location
{12/2020 - 07/2021} % Date
\begin{cvitems}
\item {As a contract research project which has assigned to department of Cyber Security of Korea University.}
\item {Found several vulnerabilities and exploits including Stored XSS, Information disclosure, open redirect, etc at one of Korea's largest game companies' web services.}
\end{cvitems}

